---
title: "Teaching" 
layout: splash
class: wide 
---


```{r setup, include=FALSE}
library(highcharter) 
library(dplyr)
library(htmlwidgets)

sample_data <- data.frame(
  "Classes" = c("EC 313 Summer 2018","EC 313 Fall 2018","EC 313 Spring 2020","EC 202 Fall 2019"),
  "My_Score" =  c(4.0, 4.0, 4.6, 4.6),
  "Historic_Average" = c(4.0, 4.0, 4.0, 3.9),
  stringsAsFactors = F
)

categories_column <- "Classes"
measure_columns <- c("My_Score","Historic_Average")

base_highchart <- highchart() %>%
  hc_xAxis(categories = sample_data[,categories_column],
           title = categories_column) %>%
  hc_add_series(name = measure_columns[1],
                data = sample_data[,measure_columns[1]]) %>%
  hc_add_series(name = measure_columns[2],
                data = sample_data[,measure_columns[2]]) %>%
  hc_title(text = "Instructional Quality by Course", margin = 20, align = "left")

hc<- base_highchart %>% hc_chart(type = "column")
```

# Teaching
---

## As an Independent Instructor:

<div style="width:50%; height:500px;float:left" markdown="1"> 
```{r, include=TRUE, echo=FALSE}
hc_size(hc, width="400px", height = "350px")
```
</div>

<div style="width:50%; height:500px;float:right" markdown="1"> 

**EC313:** *Intermediate Macroeconomics*
   Summer 2018, Fall 2018, Spring 2020  
   Syllabus: [*Original*](../images/EC313_F2018.pdf), [*COVID-19 Version*](../images/EC313_SP20.pdf)
   
**EC202:** *Principles of Macroeconomics*&mdash;Fall 2019  
  Syllabus: [*Infographic Version*](../images/ec202-fall2019_40286598.pdf), [*Text Version*](../images/EC202_F19.pdf)
  
</div> 



### Selected Student Feedback



  
## As a Graduate Assistant 

| **Class** |  **Term(s)** | **Duties** |
|---|---|---|
|**EC 201:** *Principles of Microeconomics*| Fall 2016, Spring 2018 | Lead disscussion sections |  
|**EC 202:** *Principles of Macroeconomics* | Winter 2017 | Lead disscussion sections |  
|**EC 423/523:** *Econometrics*  | Fall 2017  (*First Year PhD course*) | Lead disscussion sections |   
|**EC 313:** *Intermediate Macroeconomics* | Fall 2017, Winter 2018| Graded Student Assignments |
|**EC 422/522:** *Forecasting* | Winter 2018, Winter 2019 | Graded Student Coding Assignments |
|**EC 420/520:** *Computational Macro.* | Spring 2019| Graded Student Coding Assignments |


